### 2024-04-16 docs/projects/data-processing/index.qmd
many json lines - rendered

In this series of notebooks, we explore [ggplot2](https://ggplot2.tidyverse.org/), a famous R package for grammar-of-graphics data visualization, from within Clojure.

@@

```{=html}
<div><pre><small><small>source: <a href="https://github.com/scicloj/clojure-data-scrapbook/blob/main/projects/datavis/ggplot/notebooks/index.clj">projects/datavis/ggplot/notebooks/index.clj</a></small></small></pre></div>
```

>>>>

These notes offers various demonstrations of data processing in Clojure.

@@

```{=html}
<div><pre><small><small>source: projects/data-processing/notebooks/index.clj</small></small></pre></div>
```
